Supporting Information:\\ NMRlipids IV: Headgroup \& glycerol backbone structures, and cation binding in bilayers with PS lipids

### 2019-04-23 Manuscript/manuscriptPSsuppl.tex
Fix concentration in Fig. S18 as mentioned here: https://github.com/NMRLipids/NMRlipidsIVotherHGs/issues/69

The response of POPC headgroup order parameters to the CaCl$_2$ concentration
are underestimated in simulations of POPC:POPS (5:1) mixture with CHARMM36 when employing NBfix (as obtained from CHARMM_GUI in January 2018) for interactions between calcium and lipid oxygens \cite{kim16}
(Fig. \ref{changesWITHCaClPS} in the main text),
indicating that the calcium binding to the bilayer is too weak with these
parameters. The response of headgroup order
parameters (Fig. \ref{OP_CHARMM_CaCl_POPC_NBFix}) and the binding affinity
(Fig. \ref{density_profile_CHARMM_CaCl_POPC_NBFix}) of calcium also to a pure
POPC bilayer are underestimated when using NBfix ions.  Notably, CHARMM36 simulations with the NBfix
terms \cite{venable13,kim16} predict similar binding affinity for sodium and calcium. Without the NBfix term, the calcium binding affinity to pure POPC lipid bilayers was overestimated in the CHARMM36 model \cite{catte16}.

@@

\pagebreak
\section{Calcium density profiles from simulations with \\ POPC:POPS(5:1) mixture}
\todo{This section could benefit from some clarifying text}
\begin{figure}[ht]
  \centering
  \includegraphics[width=10cm]{../Figs/CAdensPCPSmixture.eps}
  \caption{\label{CAdensPCPSmixtureALL}
    Number density profiles of Ca$^{2+}$ from POPC:POPS (5:1) mixtures simulated with different force fields. The ion densities are taken along the z-axis that coincides with the bilayer normal. 
  }
  \todo{Should we include also counterions into the plot?} \\
  \todo{It would be helpful to have the panels in the same order as in the main text}
  \todo{Concentration for C36 here is smaller than in main text}

\end{figure}

>>>>

The response of POPC headgroup order parameters to the CaCl$_2$ concentration
are underestimated in simulations of POPC:POPS (5:1) mixture with CHARMM36 when employing NBfix (as obtained from CHARMM\_GUI in January 2018) for interactions between calcium and lipid oxygens \cite{kim16}
(Fig. \ref{changesWITHCaClPS} in the main text),
indicating that the calcium binding to the bilayer is too weak with these
parameters. The response of headgroup order
parameters (Fig. \ref{OP_CHARMM_CaCl_POPC_NBFix}) and the binding affinity
(Fig. \ref{density_profile_CHARMM_CaCl_POPC_NBFix}) of calcium also to a pure
POPC bilayer are underestimated when using NBfix ions.  Notably, CHARMM36 simulations with the NBfix
terms \cite{venable13,kim16} predict similar binding affinity for sodium and calcium. Without the NBfix term, the calcium binding affinity to pure POPC lipid bilayers was overestimated in the CHARMM36 model \cite{catte16}.

@@

\pagebreak
\section{Calcium density profiles from simulations with \\ POPC:POPS(5:1) mixture}
\todo{This section could benefit from some clarifying text}
\begin{figure}[ht]
  \centering
  \includegraphics[width=10cm]{../Figs/CAdensPCPSmixture.eps}
  \caption{\label{CAdensPCPSmixtureALL}
    Number density profiles of Ca$^{2+}$ from POPC:POPS (5:1) mixtures simulated with different force fields. The ion densities are taken along the z-axis that coincides with the bilayer normal. 
  }
  \todo{Should we include also counterions into the plot?} \\
  \todo{It would be helpful to have the panels in the same order as in the main text}
\end{figure}
